Manuscript Code

### 2022-09-27 Manuscript Code.Rmd
Calculating study region areas and de-centering income analyses from affluence

@@

@@

census_preds_wide %>%
  group_by(income_group) %>%
  summarise(pop = sum(bk_tot_pop_2010),
            ufp = weighted.mean(pnc_noscreen, bk_tot_pop_2010),
            ufp_pct_diff = per_diff(ufp, 5712),
            bc = weighted.mean(ma200_ir_bc1, bk_tot_pop_2010),
            bc_pct_diff = per_diff(bc, 453),
            no2 = weighted.mean(no2, bk_tot_pop_2010),
            no2_pct_diff = per_diff(no2, 7.63),
            pm2.5 = weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010),
            pm2.5_pct_diff = per_diff(pm2.5, 4.27))

@@

## Pollution means weighted by block population divided by number of grades block is assigned to
redlining_blocks %>%
  group_by(holc_grade) %>%
  summarise(ufp = weighted.mean(pnc_noscreen, bk_tot_pop_2010/count),
            ufp_pct_diff = per_diff(ufp, 7150),
            bc = weighted.mean(ma200_ir_bc1, bk_tot_pop_2010/count),
            bc_pct_diff = per_diff(bc, 547),
            no2 = weighted.mean(no2, bk_tot_pop_2010/count),
            no2_pct_diff = per_diff(no2, 9.29),
            pm2.5 = weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010/count),
            pm2.5_pct_diff = per_diff(pm2.5, 4.75))

@@

new_census_preds_wide %>%
  group_by(new_income_group) %>%
  summarise(pop = sum(bk_tot_pop_2010),
            ufp = weighted.mean(pnc_noscreen, bk_tot_pop_2010),
            ufp_pct_diff = per_diff(ufp, 5584),
            bc = weighted.mean(ma200_ir_bc1, bk_tot_pop_2010),
            bc_pct_diff = per_diff(bc, 446.7),
            no2 = weighted.mean(no2, bk_tot_pop_2010),
            no2_pct_diff = per_diff(no2, 7.52),
            pm2.5 = weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010),
            pm2.5_pct_diff = per_diff(pm2.5, 4.259))

cor(new_census_preds_wide$bg_med_inc_hshld.x, new_census_preds_wide$med_HH_inc_2019)

@@

redlining_blocks_unique <- subset(redlining_blocks, !duplicated(redlining_blocks$block_key))

>>>>

## Study region area
all_block_areas <- read.csv("/projects/trap/transfer/kaya/block areas.csv")
all_block_areas$BLOCKID10 <- as.character(all_block_areas$BLOCKID10)
census_block_areas <- census_preds_wide %>%
  left_join(all_block_areas, by=c("block_key"="BLOCKID10"))
sum(census_block_areas$area/1000000)

## Redlining region area
redlining_blocks_unique <- subset(redlining_blocks, !duplicated(redlining_blocks$block_key))
redlining_block_areas <- redlining_blocks_unique %>%
  left_join(all_block_areas, by=c("block_key"="BLOCKID10"))
sum(redlining_block_areas$area/1000000)

## Redlining grades area
redlining_grades_areas <- redlining_blocks %>%
  left_join(all_block_areas, by=c("block_key"="BLOCKID10"))
redlining_grades_areas$adj_area <- redlining_grades_areas$area/redlining_grades_areas$count
sum(redlining_grades_areas[redlining_grades_areas$holc_grade == "A", ]$adj_area/1000000)
sum(redlining_grades_areas[redlining_grades_areas$holc_grade == "B", ]$adj_area/1000000)
sum(redlining_grades_areas[redlining_grades_areas$holc_grade == "C", ]$adj_area/1000000)
sum(redlining_grades_areas[redlining_grades_areas$holc_grade == "D", ]$adj_area/1000000)
sum(redlining_grades_areas[redlining_grades_areas$holc_grade == "X", ]$adj_area/1000000)

@@

## Pollutant correlations

cor(census_preds_wide[, c('ma200_ir_bc1','no2', 'pnc_noscreen', 'pm2.5_ug_m3')], method='pearson')

@@

census_preds_wide %>%
  group_by(income_group) %>%
  summarise(pop = sum(bk_tot_pop_2010),
            ufp = signif(weighted.mean(pnc_noscreen, bk_tot_pop_2010), digits=3),
            ufp_pct_diff = per_diff(ufp, 6680),
            bc = signif(weighted.mean(ma200_ir_bc1, bk_tot_pop_2010), digits=3),
            bc_pct_diff = per_diff(bc, 520),
            no2 = round(weighted.mean(no2, bk_tot_pop_2010), digits=1),
            no2_pct_diff = per_diff(no2, 8.7),
            pm2.5 = round(weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010), digits=1),
            pm2.5_pct_diff = per_diff(pm2.5, 4.6))

@@

## Pollution means weighted by block population divided by number of grades block is assigned to
redlining_blocks %>%
  group_by(holc_grade) %>%
  summarise(pop = sum(bk_tot_pop_2010/count),
            ufp = weighted.mean(pnc_noscreen, bk_tot_pop_2010/count),
            ufp_pct_diff = per_diff(ufp, 7150),
            bc = weighted.mean(ma200_ir_bc1, bk_tot_pop_2010/count),
            bc_pct_diff = per_diff(bc, 547),
            no2 = weighted.mean(no2, bk_tot_pop_2010/count),
            no2_pct_diff = per_diff(no2, 9.29),
            pm2.5 = weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010/count),
            pm2.5_pct_diff = per_diff(pm2.5, 4.75))

@@

new_census_preds_wide %>%
  group_by(new_income_group) %>%
  summarise(pop = sum(bk_tot_pop_2010),
            ufp = signif(weighted.mean(pnc_noscreen, bk_tot_pop_2010), digits=3),
            ufp_pct_diff = per_diff(ufp, 6680),
            bc = signif(weighted.mean(ma200_ir_bc1, bk_tot_pop_2010), digits=3),
            bc_pct_diff = per_diff(bc, 520),
            no2 = round(weighted.mean(no2, bk_tot_pop_2010), digits=1),
            no2_pct_diff = per_diff(no2, 8.7),
            pm2.5 = round(weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010), digits=1),
            pm2.5_pct_diff = per_diff(pm2.5, 4.6))

@@
